Graph Data Generators for Data Science: A Survey

### 2018-05-30 main.tex
Merging of sections 3 and 4
fixed the compilation problem
changed title; added an abstract

% Title portion
\title{Graph Data Generators in the World of Big Data}
\author{
ANGELA BONIFATI
\affil{Lyon 1 University, France}
IRENA HOLUBOV\'{A}
\affil{Charles University, Prague, Czech Republic}
ARNAU PRAT-P\'{E}REZ
\affil{DAMA-UPC, Universitat Polit\`ecnica de Catalunya, Spain}
SHERIF SAKR
\affil{King Saud bin Abdulaziz University for Health Sciences, Saudi Arabia}
}
% NOTE! Affiliations placed here should be for the institution where the
%       BULK of the research was done. If the author has gone to a new
%       institution, before publication, the (above) affiliation should NOT be changed.
%       The authors 'current' address may be given in the "Author's addresses:" block (below).
%       So for example, Mr. Abdelzaher, the bulk of the research was done at UIUC, and he is
%       currently affiliated with NASA.

\begin{abstract}
In recent years the term Big Data has become a phenomenon that breaks down borders of many technologies and approaches that have so far been acknowledged as mature and robust.

...

@@

\input{introduction}
\input{preliminaries}
\input{comparison}
\input{classification}
\input{generators}
%\input{comparison2}
\input{challenges}
\input{conclusion}

>>>>

% Title portion
%\title{Graph Data Generators in the World of Big Data}
\title{Graph Data Generators for Data Science: A Survey}
\author{
ANGELA BONIFATI
\affil{Lyon 1 University, France}
IRENA HOLUBOV\'{A}
\affil{Charles University, Prague, Czech Republic}
ARNAU PRAT-P\'{E}REZ
\affil{DAMA-UPC, Universitat Polit\`ecnica de Catalunya, Spain}
SHERIF SAKR
\affil{King Saud bin Abdulaziz University for Health Sciences, Saudi Arabia}
}
% NOTE! Affiliations placed here should be for the institution where the
%       BULK of the research was done. If the author has gone to a new
%       institution, before publication, the (above) affiliation should NOT be changed.
%       The authors 'current' address may be given in the "Author's addresses:" block (below).
%       So for example, Mr. Abdelzaher, the bulk of the research was done at UIUC, and he is
%       currently affiliated with NASA.

\begin{abstract}
%In recent years the term Big Data has become a phenomenon that breaks down borders of many technologies and approaches that have so far been acknowledged as mature and robust.
%...
The abundance of interconnected data has fueled the design and
implementation of graph generators reproducing real-world
properties, 
or gauging the effectiveness of graph algorithms, graph tools and 
applications manipulating these data.
We consider graph generation targeting multiple subfields, such as graph databases, graph data mining ,
graph streaming and machine learning communities, alongside community
detection,
social networks and IoT communities. 
Despite the disparate requirements of graph generators throughout these
communities, we analyze them under a common umbrella, reaching out the
functionalities, the practical usage, and the supported operations of graph generators. 
We argue that
this classification is serving the need of providing data scientists,
researchers and practitioners with the right data generator at hand.

This survey provides a comprehensive overview of the state-of-the-art graph generators 
by focusing on those that are pertinent for data science tasks. Finally, we discuss
open challenges and missing features of graph generators in view of the 
evolving requirements in data science.

@@

\input{introduction}
\input{preliminaries}
\input{comparison}
%\input{classification}
\input{generators}
%\input{comparison2}
\input{challenges}
\input{conclusion}
